Iterative forecasting and the trap of self-fulfilling prophecies

### 2021-04-13 manuscript/manuscript.Rmd
double-space char
no `nbsp;`
re-knit

fig1ab <- predictions %>% 
  filter(reps == "2", time < 10) %>%
  ggplot(aes(time, col = model, fill = model)) + 
  geom_point(aes(y = expected)) + 
  geom_errorbar(aes(ymin = low, ymax = high)) +
  geom_point(aes(y = true), pch = "*", size = 12, 
             alpha = 0.6) + 
  facet_wrap(~scenario, ncol = 1, labeller =as_labeller(c(
    A_unfished = "A. Without fishing",
    B_fished = "B. Managed harvest"))) +
  ylab("stock size")
 
 
 
 fig1ab + fig1cd + 
  plot_layout(widths =  c(3,1), guides = 'collect') + 
  theme(plot.margin = margin(0, 0, .1, .1, "cm"))
```

@@

The author acknowledges support from NSF CAREER Award #1942280 and helpful discussions with Melissa Chapman and Jeremy Fox.

>>>>

fig1ab <- predictions %>% 
  filter(reps == "2", time < 10) %>%
  ggplot(aes(time, col = model, fill = model)) + 
  geom_point(aes(y = expected)) + 
  geom_errorbar(aes(ymin = low, ymax = high)) +
  geom_point(aes(y = true), pch = "*", size = 12, 
             alpha = 0.6) + 
  facet_wrap(~scenario, ncol = 1, labeller =as_labeller(c(
    A_unfished = "A. Without fishing",
    B_fished = "B. Managed harvest"))) +
  ylab("stock size")

fig1ab + fig1cd + 
  plot_layout(widths = c(3,1), guides = 'collect') + 
  theme(plot.margin = margin(0, 0, .1, .1, "cm"))
```

@@

The author acknowledges support from NSF CAREER Award #1942280 and helpful discussions with Melissa Chapman, Jeremy Fox, and anonymous reviewers.
